### 2018-05-25 Paper/method.tex
..

%%%%%%%%%%% Revised %%%%%%%%%%%
\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
\Require $\tau > 0$, $\tau_\text{screen} > 0$,
$s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
\Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
    \Procedure{Screening}{}
    %  \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
     %  according to the probability density $\bm{f(\theta)}$.
     %   \State $N_\text{total} = N_\text{total} + n_1$.
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k~=~N_\text{total}+1, \ldots, N_\text{total}+n_1$. 
      \State $N_\text{total} = N_\text{total} + n_1$
      \State Compute 
      $\mu_{1, i} = \frac{1}{N_\text{total}} \sum_{k = 1}^{N_\text{total}} (g^k_i)^2$
      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
             $i = 1, \ldots, \Np$. 
      \State Determine initial ranks: 
            let $\mathcal{R}^{old} = \{ \nu_{i_1}, \nu_{i_2}, \ldots, \nu_{i_\Np}\}$ such that 
\[
   \nu_{i_1} \geq \nu_{i_2} \geq \cdots \geq \nu_{i_\Np}. 
\]
      \State Set $s$ = 1.
      \State Set $\mathrm{done} = \mathrm{false}$.
      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
        \State $s = s + 1$.
        \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
       \State $N_\text{total} = N_\text{total} + n_s$.
        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.

@@

Based on the steps outlined in the above algorithm, it can be said that the set
of sample points used for estimating the screening metric,
$\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks between
successive iterations as well as a certain degree of convergence in estimates
of the screening metric for each uncertain parameter is accomplished. However,
the amount of computational effort associated the screening process is limited
by the choice of maximum number of iterations, $s_\text{max}$. 
Key inputs
are as follows: (1) 
a limiting value $\tau$ of the maximum relative change in the sensitivity
measure between succesive iterations; (2) 
a limiting ratio $\tau_\text{screen}$ of the sensitivity metric 
relative to its maximum value;
(3) a real number $\beta \in (0, 1)$ to 
guide the number of new samples $\lceil \beta n_1 \rceil$ 
at each iteration ($\lceil \beta n_1
\rceil$ 
is the smallest integer greater than or equal to $\beta n_1$); 
(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
for the initial screening step in
the algorithm and the corresponding gradient evaluations 
$\{ \bm{g}^k \}_{k=1}^{n_0}$, where
$\bm{g}^k = \nabla_{\bm{\theta}} G(\bm{\theta}_k)$. 
The outputs are the set of active
indices $\mathcal{I}_\text{active}$ corresponding to the 
\emph{important parameters}, the total number of available model 
evaluations $N_\text{total}$, and the enriched set of gradient evaluations 
$\{ \bm{g}^k\}_{k=1}^{N_\text{total}}$. 
Parameter screening is an integral part of the
overall surrogate model construction framework 
detailed below.

@@

\node (fss) [process, below of=sam0, text width=14.5em, yshift=-0.5cm] {Construct regression-based 
surrogate in full-space (FSS) uing ($N_\text{total}$+$n_1$) model evaluations};

@@

The available set of model evaluations are utlized and further enhanced during
parameter screening as discussed earlier.  At the end of screening, the set of
active indices, $\mathcal{I}_\text{active}$, is used to evaluate $\alpha$ in the
following equation: 
%
\be
\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p},
\label{eq:alpha}
\ee
%
where $|\mathcal{I}_\text{active}|$ denotes the cardinality of
$\mathcal{I}_\text{active}$.  Scope for dimension-reduction increases as
$\alpha$ decreases.  Hence, if $\alpha$ is considered to be small and
computational gains are expected owing to dimension reduction, the ROS is
constructed and verified for accuracy using a combination of model evaluations
used for screening and those associated with the validation test suite.  On the
other hand, if $\alpha$ is close to 1, the set of inputs required for screening are
 updated as needed, and a
new set of $n_0$ samples and corresponding model evaluations are generated. The
FSS is re-constructed using the enriched set of evaluations and the
aforementioned analysis is repeated as illustrated in the flow-diagram
in Figure~\ref{fig:flow} that shows the overall 
parameter screening and surrogate model construction method.

>>>>

%%%%%%%%%%% Revised %%%%%%%%%%%
\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
\Require $\tau > 0$, $\tau_\text{screen} > 0$,
$s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
\Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
    \Procedure{Screening}{}
    %  \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
     %  according to the probability density $\bm{f(\theta)}$.
     %   \State $N_\text{total} = N_\text{total} + n_1$.
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k~=~N_\text{total}+1, \ldots, N_\text{total}+n_1$. 
      \State $N_\text{total} = N_\text{total} + n_1$
      \State Compute 
      $\mu_{1, i} = \frac{1}{N_\text{total}} \sum_{k = 1}^{N_\text{total}} (g^k_i)^2$
      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
             $i = 1, \ldots, \Np$. 
      \State Determine initial ranks: 
            let $\mathcal{R}^{old} = \{ \nu_{i_1}, \nu_{i_2}, \ldots, \nu_{i_\Np}\}$ such that 
\[
   \nu_{i_1} \geq \nu_{i_2} \geq \cdots \geq \nu_{i_\Np}. 
\]
      \State Set $s$ = 1.
      \State Set $\mathrm{done} = \mathrm{false}$.
      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
        \State $s = s + 1$.
        \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
       \State $N_\text{total} = N_\text{total} + n_s$.
        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.

@@

Based on the steps outlined in the above algorithm, it can be said that the set
of sample points used for estimating the screening metric,
$\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks between
successive iterations as well as a certain degree of convergence in estimates
of the screening metric for each uncertain parameter is accomplished. However,
the amount of computational effort associated the screening process is limited
by the choice of maximum number of iterations, $s_\text{max}$. 
Key inputs
are as follows: (1) 
a limiting value $\tau$ of the maximum relative change in the sensitivity
measure between successive iterations; (2) 
a limiting ratio $\tau_\text{screen}$ of the sensitivity metric 
relative to its maximum value;
(3) a real number $\beta \in (0, 1)$ to 
guide the number of new samples $\lceil \beta n_1 \rceil$ 
at each iteration ($\lceil \beta n_1
\rceil$ 
is the smallest integer greater than or equal to $\beta n_1$); 
(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
for the initial screening step in
the algorithm and the corresponding gradient evaluations 
$\{ \bm{g}^k \}_{k=1}^{n_0}$, where
$\bm{g}^k = \nabla_{\bm{\theta}} G(\bm{\theta}_k)$. 
The outputs are the set of active
indices $\mathcal{I}_\text{active}$ corresponding to the 
\emph{important parameters}, the total number of available model 
evaluations $N_\text{total}$, and the enriched set of gradient evaluations 
$\{ \bm{g}^k\}_{k=1}^{N_\text{total}}$. 
Parameter screening is an integral part of the
overall surrogate model construction framework 
detailed below.

@@

\node (fss) [process, below of=sam0, text width=14.5em, yshift=-0.5cm] {Construct regression-based 
surrogate in full-space (FSS) using ($N_\text{total}$+$n_1$) model evaluations};

@@

The available set of model evaluations are utilized and further enhanced during
parameter screening as discussed earlier.  At the end of screening, the set of
active indices, $\mathcal{I}_\text{active}$, is used to evaluate $\alpha$ in the
following equation: 
%
\be
\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p},
\label{eq:alpha}
\ee
%
where $|\mathcal{I}_\text{active}|$ denotes the cardinality of
$\mathcal{I}_\text{active}$.  Scope for dimension-reduction increases as
$\alpha$ decreases.  Hence, if $\alpha$ is considered to be small and
computational gains are expected owing to dimension reduction, the ROS is
constructed and verified for accuracy using a combination of model evaluations
used for screening and those associated with the validation test suite.  On the
other hand, if $\alpha$ is close to 1, the set of inputs required for screening are
 updated as needed, and a
new set of $n_0$ samples and corresponding model evaluations are generated. The
FSS is re-constructed using the enriched set of evaluations and the
aforementioned analysis is repeated as illustrated in the flow-diagram
in Figure~\ref{fig:flow} that shows the overall 
parameter screening and surrogate model construction method.
